Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-06-18 AM+draft.tex
19June18 morning commit - results - simulation

>>>>

In answer to the question of how well Eagle finds true snp-trait associations and avoids false snp-trait associations, we calculated, empirically, 
the statistical power and false discovery rate of the different methods across the six scenarios. We did this by recording the set of snp that had been selected when generating a 
replicate's trait data. These snp are in true association with the trait. Also, each replicate had a different set of selected snp. 
When the data were analysed via a particular method, 
we were able to determine for that method which of its snp-trait findings were true and which were false. A snp finding was deemed to be true if it was positioned within 40kb of the location of a true snp.

We did this by recording, at the time a replicate was generated, those snp which had been selected to 
have an additive effect on the quantitative trait. These snp are the true snp in association with the trait. When we analysed a
replicate by each of the methods, we also recorded the number of snp reported to be in significant association with the trait. 
Those snp findings that were positioned within 40 kb of the location of a true snp were deemed as true findings.  Hence, 
for each method for a given replicate, we were able to record the number of true and false findings.
